Measuring individual differences in the understanding of gaze cues

### 2022-08-10 paper/manuscript.Rmd
complete run through script on stats server

```{r setup, include = FALSE}
library("papaja")
# r_refs("r-references.bib")
```

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
```

>>>>

```{r setup, include = FALSE}
library("papaja")
library(ggplot2)
theme_set(theme_classic())
# r_refs("r-references.bib")
```

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
hedge_variation_plot_GLMM <- readRDS(file = "../saves/gafo-hedge-variation-plot-GLMM.rds")
box_variation_plot_GLMM <- readRDS(file = "../saves/gafo-box-variation-plot-GLMM.rds")
box_variation_plot_GLMM

knitr::include_graphics(c("../figures/gafo_results.png"))
```
